---
title: "pixelTidy"
author: "Yuting Chen"
date: "2022/2/14"
output: html_document
---

```{r}
library(tidyverse)
```

# Tidy first data set

```{r}
aerial <- read_csv("../data/AdoptAPixel3km2020_100m_aerialImageryLabels.csv")
```

```{r}
# The values of variables are the same, but ceoFLAGGED is different
aerial %>% 
  select(SIZE_M, PLOTSHAPE, ceoFLAGGED, SAMPLE_POINTS) %>% 
  unique()
```
```{r}
# See the ceoFLAGGED data
aerial %>% 
  filter(ceoFLAGGED == TRUE)
```


```{r}
# Delete some variables that have the same values in it.
Aerial <- aerial %>% 
  select(-SIZE_M, -PLOTSHAPE, -ceoFLAGGED, -SAMPLE_POINTS)
View(Aerial)
```

```{r}
#Aerial %>% 
#  write_csv("../finalData/Aerial.csv")
```

```{r}
 Aerial %>% 
          pivot_longer(cols = 7:19,
                       names_to = "feature",
                       values_to = "percentage") %>% 
          mutate(feature = str_replace(feature, "ceo", ""),
                 percentage = round(percentage, 1)) %>% 
          filter(AOI_NUM %in% c(2, 3, 5) & ceoPLOT_NUM %in% c(5, 7, 9)) %>% 
          filter(percentage != 0) %>% 
  group_by(feature) %>% 
  mutate(sum_per = sum(percentage, na.rm = TRUE)) %>% 
    mutate(final_per = round(percentage/sum_per*100, 2)) %>% 
  ggplot(aes(x = feature, y = percentage, fill = as.factor(seesAOIplot))) +
  geom_col(position = "fill") +
  geom_text(aes(label=paste0(final_per,"%")),
                     position=position_fill(vjust=0.5), colour="white", size =2)
  #geom_text(aes(y = label_y, label = percentage), colour = "white")

```
%>% 
  ggplot(aes(x = feature, y = percentage, fill = as.factor(seesAOIplot))) +
  geom_col(position = "fill") +
  geom_text(aes(label=paste0(percentage,"%")),
                     position=position_fill(vjust=0.5), colour="white", size =2)
  #geom_text(aes(y = label_y, label = percentage), colour = "white")


### Tidy second data set

```{r}
pictures <- read_csv("../data/AdoptAPixel3km2020_GO_LandCover.csv")
```

```{r}
pictures <- pictures %>% 
  select(-landcoversDataSource, -landcoversMucCode, -landcoversMucDetails, -landcoversDownwardExtraData, -landcoversEastExtraData, -landcoversNorthExtraData, -landcoversSouthExtraData, -landcoversUpwardExtraData, -landcoversWestExtraData) 
View(pictures)
```

```{r}
#pictures %>% 
#  write_csv("../finalData/pictures.csv")
```



```{r}
AOI <- Aerial %>% 
  select(AOI_NUM) %>% 
  unique()
```

```{r}
pictures %>% 
  select(landcoversDataSource, landcoversMucCode, landcoversMucDetails, landcoversDownwardExtraData, landcoversEastExtraData, landcoversNorthExtraData, landcoversSouthExtraData, landcoversUpwardExtraData, landcoversWestExtraData) 
```

# Pie Chart

```{r}
library(ggthemes)
Aerial %>% 
  pivot_longer(cols = 7:19,
               names_to = "feature",
               values_to = "percentage") %>% 
  mutate(feature = str_replace(feature, "ceo", ""),
         percentage = round(percentage, 1)) %>% 
  filter(AOI_NUM %in% c(2, 3) & ceoPLOT_NUM %in% c(7,9)) %>% 
  filter(percentage != 0) %>% 
  ggplot(aes(x = "", y = percentage, fill = feature)) +
  geom_col() +
  geom_text(aes(label = percentage),
            position = position_stack(vjust = 0.5),
            size = 3,
            show.legend = FALSE) +
  coord_polar(theta = "y") +
  facet_wrap(~seesAOIplot) +
  labs(title = "The percentage of features in each plot",
       x = "",
       y = "") +
  guides(fill = guide_legend(title = "Features")) +
  scale_fill_viridis_d() +
  theme_void()
  
```



# Bar chart

```{r}
Aerial %>% 
  pivot_longer(cols = 7:19,
               names_to = "feature",
               values_to = "percentage") %>% 
  mutate(feature = str_replace(feature, "ceo", ""),
         percentage = round(percentage, 1)) %>% 
  filter(AOI_NUM %in% c(2, 3) & ceoPLOT_NUM %in% c(7,9)) %>% 
  filter(percentage != 0) %>% 
  ggplot(aes(x = feature, y = percentage, fill = as.factor(seesAOIplot))) +
  geom_col(position = "fill") +
  labs(title = "The proportion of each feature in all plots",
       x = "",
       y = "Percentage") +
  guides(fill = guide_legend(title = "Plots")) +
  coord_flip() +
  theme_bw()
  
```




```{r}
pictures <- read_csv("../finalData/pictures.csv")
```

## Pictures 1-Location

```{r}
location <- pictures %>% 
  select(OBJECTID, landcoversLandCoverId, landcoversMeasuredAt, siteName, landcoversMeasurementLatitude, landcoversMeasurementLongitude, elevation, landcoversMeasurementElevation, landcoversMucDescription) %>% 
  rename(LandCoverID = landcoversLandCoverId,
         MeasuredTime = landcoversMeasuredAt,
         SiteName = siteName,
         MeasuredLatitude = landcoversMeasurementLatitude,
         MeasuredLogitude = landcoversMeasurementLongitude,
         Elevation = elevation,
         MeasuredElevation = landcoversMeasurementElevation,
         MucDescription = landcoversMucDescription)

#location %>% 
#  write_csv("../finalData/location.csv")
```


## Pictures 2-Downward

```{r}
downward <- 
  pictures %>% 
  select(OBJECTID, contains("Downward")) %>% 
  mutate(thumbUrl = str_replace(landcoversDownwardPhotoUrl, "original", "thumb")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_extract(thumbUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadThumbPicture = str_replace_all(DownloadThumbPicture, "/", "_")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_c("golc", "thumb", DownloadThumbPicture, sep = "_"),
                                       "null")) %>% 
  rename("DownwardOriginalUrl" = landcoversDownwardPhotoUrl) %>% 
  mutate(DownloadOriginalPicture = ifelse(!DownwardOriginalUrl %in% c("null", "rejected"),
                                       str_extract(DownwardOriginalUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadOriginalPicture = str_replace_all(DownloadOriginalPicture, "/", "_")) %>% 
  mutate(DownloadOriginalPicture = ifelse(!DownwardOriginalUrl %in% c("null", "rejected"),
                                       str_c("golc", DownloadOriginalPicture, sep = "_"),
                                       "null")) %>% 
  select(OBJECTID, thumbUrl, DownloadThumbPicture, DownwardOriginalUrl, DownloadOriginalPicture)

#downward %>% 
#  write_csv("../finalData/downward.csv")
```

## Pictures 3-East

```{r}
east <- 
  pictures %>% 
  select(OBJECTID, contains("East")) %>% 
  mutate(thumbUrl = str_replace(landcoversEastPhotoUrl, "original", "thumb")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_extract(thumbUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadThumbPicture = str_replace_all(DownloadThumbPicture, "/", "_")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_c("golc", "thumb", DownloadThumbPicture, sep = "_"),
                                       "null")) %>% 
  rename("EastOriginalUrl" = landcoversEastPhotoUrl) %>% 
  mutate(DownloadOriginalPicture = ifelse(!EastOriginalUrl %in% c("null", "rejected"),
                                       str_extract(EastOriginalUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadOriginalPicture = str_replace_all(DownloadOriginalPicture, "/", "_")) %>% 
  mutate(DownloadOriginalPicture = ifelse(!EastOriginalUrl %in% c("null", "rejected"),
                                       str_c("golc", DownloadOriginalPicture, sep = "_"),
                                       "null")) %>% 
  select(OBJECTID, landcoversEastClassifications, thumbUrl, DownloadThumbPicture, EastOriginalUrl, DownloadOriginalPicture)

#east %>% 
#  write_csv("../finalData/east.csv")
```

## Pictures 4-North

```{r}
#north <- 
  pictures %>% 
  select(OBJECTID, contains("North")) %>% 
  mutate(thumbUrl = str_replace(landcoversNorthPhotoUrl, "original", "thumb")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_extract(thumbUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadThumbPicture = str_replace_all(DownloadThumbPicture, "/", "_")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_c("golc", "thumb", DownloadThumbPicture, sep = "_"),
                                       "null")) %>% 
  rename("NorthOriginalUrl" = landcoversNorthPhotoUrl) %>% 
  mutate(DownloadOriginalPicture = ifelse(!NorthOriginalUrl %in% c("null", "rejected"),
                                       str_extract(NorthOriginalUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadOriginalPicture = str_replace_all(DownloadOriginalPicture, "/", "_")) %>% 
  mutate(DownloadOriginalPicture = ifelse(!NorthOriginalUrl %in% c("null", "rejected"),
                                       str_c("golc", DownloadOriginalPicture, sep = "_"),
                                       "null")) %>% 
  select(OBJECTID, landcoversNorthClassifications, thumbUrl, DownloadThumbPicture, NorthOriginalUrl, DownloadOriginalPicture)
  
  


#north %>% 
#  write_csv("../finalData/north.csv")
```


## Pictures 5-South

```{r}
south <-
  pictures %>% 
  select(OBJECTID, contains("South")) %>% 
  mutate(thumbUrl = str_replace(landcoversSouthPhotoUrl, "original", "thumb")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_extract(thumbUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadThumbPicture = str_replace_all(DownloadThumbPicture, "/", "_")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_c("golc", "thumb", DownloadThumbPicture, sep = "_"),
                                       "null")) %>% 
  rename("SouthOriginalUrl" = landcoversSouthPhotoUrl) %>% 
  mutate(DownloadOriginalPicture = ifelse(!SouthOriginalUrl %in% c("null", "rejected"),
                                       str_extract(SouthOriginalUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadOriginalPicture = str_replace_all(DownloadOriginalPicture, "/", "_")) %>% 
  mutate(DownloadOriginalPicture = ifelse(!SouthOriginalUrl %in% c("null", "rejected"),
                                       str_c("golc", DownloadOriginalPicture, sep = "_"),
                                       "null")) %>% 
  select(OBJECTID, landcoversSouthClassifications, thumbUrl, DownloadThumbPicture, SouthOriginalUrl, DownloadOriginalPicture)

#south %>% 
#  write_csv("../finalData/south.csv")
```

## Pictures 6-Upward

```{r}
upward <- 
  pictures %>%  
  select(OBJECTID, contains("Upward")) %>% 
  mutate(thumbUrl = str_replace(landcoversUpwardPhotoUrl, "original", "thumb")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_extract(thumbUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadThumbPicture = str_replace_all(DownloadThumbPicture, "/", "_")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_c("golc", "thumb", DownloadThumbPicture, sep = "_"),
                                       "null")) %>% 
  rename("UpwardOriginalUrl" = landcoversUpwardPhotoUrl) %>% 
  mutate(DownloadOriginalPicture = ifelse(!UpwardOriginalUrl %in% c("null", "rejected"),
                                       str_extract(UpwardOriginalUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadOriginalPicture = str_replace_all(DownloadOriginalPicture, "/", "_")) %>% 
  mutate(DownloadOriginalPicture = ifelse(!UpwardOriginalUrl %in% c("null", "rejected"),
                                       str_c("golc", DownloadOriginalPicture, sep = "_"),
                                       "null")) %>% 
  select(OBJECTID, thumbUrl, DownloadThumbPicture, UpwardOriginalUrl, DownloadOriginalPicture)

#upward %>% 
#  write_csv("../finalData/upward.csv")
```

## Pictures 7-West

```{r}
west <- 
  pictures %>% 
  select(OBJECTID, contains("West")) %>% 
  mutate(thumbUrl = str_replace(landcoversWestPhotoUrl, "original", "thumb")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_extract(thumbUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadThumbPicture = str_replace_all(DownloadThumbPicture, "/", "_")) %>% 
  mutate(DownloadThumbPicture = ifelse(!thumbUrl %in% c("null", "rejected"),
                                       str_c("golc", "thumb", DownloadThumbPicture, sep = "_"),
                                       "null")) %>% 
  rename("WestOriginalUrl" = landcoversWestPhotoUrl) %>% 
  mutate(DownloadOriginalPicture = ifelse(!WestOriginalUrl %in% c("null", "rejected"),
                                       str_extract(WestOriginalUrl, "\\d{4}/\\d{2}/\\d{2}/\\d+"),
                                       "null")) %>% 
  mutate(DownloadOriginalPicture = str_replace_all(DownloadOriginalPicture, "/", "_")) %>% 
  mutate(DownloadOriginalPicture = ifelse(!WestOriginalUrl %in% c("null", "rejected"),
                                       str_c("golc", DownloadOriginalPicture, sep = "_"),
                                       "null")) %>% 
  select(OBJECTID, landcoversWestClassifications, thumbUrl, DownloadThumbPicture, WestOriginalUrl, DownloadOriginalPicture)

#west %>% 
#  write_csv("../finalData/west.csv")
```

## Pictures 8-features

```{r}
feature <- pictures %>% 
  select(OBJECTID, landcoversDryGround, landcoversFieldNotes, landcoversLeavesOnTrees, landcoversMuddy, landcoversRainingSnowing, landcoversSnowIce, landcoversStandingWater) %>% 
  select(OBJECTID, landcoversFieldNotes, everything()) %>% 
  rename(FieldNotes = landcoversFieldNotes,
         DryFround = landcoversDryGround,
         LeavesOnTrees = landcoversLeavesOnTrees,
         Muddy = landcoversMuddy,
         RainingSnowing = landcoversRainingSnowing,
         SnowIce = landcoversSnowIce,
         StandingWater = landcoversStandingWater)

#feature %>% 
#  write_csv("../finalData/feature.csv")
```


```{r}
names(pictures)
```

# Mosquito Habitats

```{r}
mosquito <- read_csv("../data/AdoptAPixel3km2020_GO_MosquitoHabitatMapper.csv")
```

```{r}
mos <- mosquito %>% 
  select(-protocol, -mosquitohabitatmapperDataSource, -mosquitohabitatmapperExtraData, -mosquitohabitatmapperMosquitoEggCount) %>% 
  rename(MapperId = mosquitohabitatmapperMosquitoHabitatMapperId,
         MeasuredTime = mosquitohabitatmapperMeasuredAt,
         MeasuredLatitude = mosquitohabitatmapperMeasurementLatitude,
         MeasuredLongitude = mosquitohabitatmapperMeasurementLongitude,
         AbdomenCloseupPhotoUrls = mosquitohabitatmapperAbdomenCloseupPhotoUrls,
         BreedingGroundEliminated = mosquitohabitatmapperBreedingGroundEliminated,
         Comments = mosquitohabitatmapperComments,
         Genus = mosquitohabitatmapperGenus,
         LarvaFullBodyPhotoUrls = mosquitohabitatmapperLarvaFullBodyPhotoUrls,
         LarvaeCount = mosquitohabitatmapperLarvaeCount,
         LastIdentifyStage = mosquitohabitatmapperLastIdentifyStage,
         Adults = mosquitohabitatmapperMosquitoAdults,
         Eggs = mosquitohabitatmapperMosquitoEggs,
         Pupae = mosquitohabitatmapperMosquitoPupae,
         Species = mosquitohabitatmapperSpecies,
         WaterSource = mosquitohabitatmapperWaterSource,
         WaterSourcePhotoUrls = mosquitohabitatmapperWaterSourcePhotoUrls,
         WaterSourceType = mosquitohabitatmapperWaterSourceType)
```


```{r}
names(mos)
```


```{r}
mosLocation <- mos %>% 
  select(OBJECTID:MeasuredLongitude)

#mosLocation %>% 
#  write_csv("../finalData/mosquitoLocation.csv")
```


```{r}
mosFeatures <- mos %>% 
  select(OBJECTID, AbdomenCloseupPhotoUrls:WaterSourceType) %>% 
  select(-contains("URL"))

#mosFeatures %>% 
#  write_csv("../finalData/mosquitoFeatures.csv")
```





### Tidy Mosquito URLs

```{r}
# Abdomen column has 4 semicolons at most
mos %>% 
  select(contains("URL")) %>% 
  mutate(abdomen = str_count(AbdomenCloseupPhotoUrls, ";")) %>% 
  arrange(desc(abdomen)) %>% 
  select(abdomen)
```

```{r}
# Larva column has 6 semicolons at most
mos %>% 
  select(contains("URL")) %>% 
  mutate(Larva = str_count(LarvaFullBodyPhotoUrls, ";")) %>% 
  arrange(desc(Larva)) %>% 
  select(Larva)
```

```{r}
# Water column has 8 semicolons at most
mos %>% 
  select(contains("URL")) %>% 
  mutate(Water = str_count(WaterSourcePhotoUrls, ";")) %>% 
  arrange(desc(Water)) %>% 
  select(Water)
```

```{r}
mosSep <- mos %>% 
  select(OBJECTID, contains("URL")) %>% 
  separate(col = AbdomenCloseupPhotoUrls,
           into = c("Abdomen1", "Abdomen2", "Abdomen3", "Abdomen4", "Abdomen5"),
           sep = ";",
           extra = "merge",
           fill = "right") %>% 
  separate(col = LarvaFullBodyPhotoUrls,
           into = c("Larva1", "Larva2", "Larva3", "Larva4", "Larva5", "Larva6", "Larva7"),
           sep = ";",
           extra = "merge",
           fill = "right") %>% 
  separate(col = WaterSourcePhotoUrls,
           into = c("Water1", "Water2", "Water3", "Water4", "Water5", "Water6", "Water7", "Water8", "Water9"),
           sep = ";",
           extra = "merge",
           fill = "right") 
mosSep 
```

```{r}
mosURL <- mosSep %>% 
  pivot_longer(cols = starts_with("Abdomen"),
               names_to = "AbdomenCloseup",
               values_to = "AbdomenCloseupPhotoUrls") %>% 
  pivot_longer(cols = starts_with("Larva"),
               names_to = "LarvaFullBody",
               values_to = "LarvaFullBodyPhotoUrls") %>% 
  pivot_longer(cols = starts_with("Water"),
               names_to = "WaterSource",
               values_to = "WaterSourcePhotoUrls") %>% 
  drop_na() %>% 
  filter(AbdomenCloseupPhotoUrls != "null" | LarvaFullBodyPhotoUrls!= "null" | WaterSourcePhotoUrls != "null") 

View(mosURL)
```

```{r}
#mosURL %>% 
#  write_csv("../finalData/mosquitoURLs.csv")
```






```{r}
mosFeatures %>% 
  select(contains("LarvaFullBodyPhotoUrls")) %>% 
  unique()
```


```{r}
names(read_csv("../finalData/mosquitoURLs.csv"))
```





























